\documentclass[a4paper,10pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{fontawesome}
\usepackage{xcolor}

\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=blue
}

\begin{document}

\centerline{\Huge \textbf{Yassin Ali}}
\vspace{2mm}
\centerline{
  Egypt, Giza, El-Haram \textbullet{}
  \href{tel:+201155015659}{\faPhone\ +201155015659} \textbullet{}
  \href{mailto:yassinalilearning77076@gmail.com}{\faEnvelope\ \texttt{yassinalilearning77076@gmail.com}} \textbullet{}
  \href{https://www.linkedin.com/in/yassin-ali-10497a252/}{\faLinkedinSquare\ Yassin Ali} \textbullet{}
  \href{https://github.com/YassenAli}{\faGithub\ YassenAli}
}

% \vspace{2mm}

\section*{Summary}
Results-driven third-year Computer Science student specializing in full-stack web development, object-oriented programming, and data structures. Proven ability to lead technical projects, mentor teams, and deliver scalable, user-focused applications. Skilled in leveraging modern frameworks to achieve tangible results, with experience in streamlining processes and exceeding expectations.

% \vspace{2mm}

\section*{Education}
\textbf{Faculty of Computers and Artificial Intelligence, Cairo University} \hfill Class of 2026 \\
Bachelor of Science in Computer Science (Information Systems Department) \\
Relevant Coursework: Databases, Data Structures \& Algorithms, Object-Oriented Programming, Logic Design, Web Development, Software Engineering, Operating Systems, Networking

% \vspace{2mm}

\section*{Experience}
\textbf{Web Development Intern, Bee Interactive} \hfill Jul 2024 -- Oct 2024 \\
\textbullet{}\hspace{2mm} Collaborated with a full-stack team on projects such as Libri (library system), Eventi (event booking system), and Montri (online course platform).  \\
\textbullet{}\hspace{2mm} Developed user-friendly interfaces and ensured seamless functionality across platforms.  \\
\textbullet{}\hspace{2mm} Delivered individual assignments including interactive applications.

\textbf{Front-End Workshop Instructor, Minders (AC Volunteer Member)} \hfill Apr 2024 -- Oct 2024 \\
\textbullet{}\hspace{2mm} Led front-end workshops, prepared educational materials, and coordinated team assignments.  \\
\textbullet{}\hspace{2mm} Acted as a liaison between students and workshop facilitators.

\textbf{Front-End Developer, Minders} \hfill Feb 2024 -- Oct 2024 \\
\textbullet{}\hspace{2mm} Worked on diverse front-end development tasks such as a Sudoku game, a personal portfolio, and advanced CSS tasks.

% \vspace{2mm}

\section*{Technical Skills}
\textbf{Programming Languages:} Python, JavaScript, Java, C++, SQL, HTML, CSS \\
\textbf{Frameworks \& Libraries:} React.js, Node.js, Django, Spring Boot \\
\textbf{Tools \& Platforms:} Git, GitHub, MySQL, MongoDB, Sequelize ORM, JUnit \\
\textbf{Other Skills:} Agile Development, Responsive Design, Version Control

% \vspace{2mm}

% \section*{Soft Skills}
% \textbf{Communication:} Ability to articulate ideas clearly and collaborate effectively in diverse team settings. \\
% \textbf{Problem-Solving:} Adept at troubleshooting, debugging, and delivering innovative solutions to complex challenges. \\
% \textbf{Leadership:} Experience mentoring teams and leading technical projects to successful completion. \\
% \textbf{Time Management:} Efficient in prioritizing tasks to meet deadlines in fast-paced environments. \\
% \textbf{Adaptability:} Quick to learn new technologies and adapt to evolving industry trends. \\
% \textbf{Teamwork:} Strong collaboration skills, fostering positive group dynamics and productivity.

% \vspace{2mm}

\section*{Projects}
\textbf{Mentoria (Online Course Platform)} \href{https://github.com/YassenAli/Mentoria}{\textcolor{blue}{(GitHub Repository)}}  \\      
\textbullet{}\hspace{2mm} Developed the back-end using Node.js and MongoDB, implementing JWT-based authentication.  \\  
\textbullet{}\hspace{2mm} Integrated Amazon S3 for secure and scalable file uploads.  \\  
\textbullet{}\hspace{2mm} Collaborated with the front-end team utilizing TypeScript for client-side development.  

\textbf{Eventi (Event Booking App)} \href{https://github.com/YassenAli/Event-System}{(GitHub Repository)}  \\
\textbullet{}\hspace{2mm} Built a robust back-end with Django and SQL for event management and user authentication.  \\
\textbullet{}\hspace{2mm} Developed features for admins to manage users and events and for users to book/cancel events.

\textbf{Libri (Book Borrow System)} \href{https://github.com/YassenAli/Libri}{(GitHub Repository)}  \\
\textbullet{}\hspace{2mm} Designed and implemented back-end functionalities using Node.js and Sequelize ORM.  \\
\textbullet{}\hspace{2mm} Created a wishlist system with hasOne and belongsToMany relationships for enhanced user experience.

\textbf{Connect Four Game} \href{https://github.com/YassenAli/XO-Game-by-CPP}{(GitHub Repository)}  \\
\textbullet{}\hspace{2mm} Developed a strategic, interactive game as part of a team project in an OOP course.  \\
\textbullet{}\hspace{2mm} Applied advanced object-oriented principles to ensure scalability and performance.

\textbf{Task Manager} \href{https://github.com/YassenAli/Task-Manager-by-CPP}{(GitHub Repository)}  \\
\textbullet{}\hspace{2mm} Implemented a task manager in C++ that lists and manages processes on Windows and Linux platforms.

\textbf{Gray-Scale Image Processor} \href{https://github.com/YassenAli/Gray-Scale-Image-Processor-by-CPP}{(GitHub Repository)}  \\
\textbullet{}\hspace{2mm} Developed an image processing software designed for manipulating grayscale and RGB images with various filters and operations.

\textbf{Online Library by C\#} \href{https://github.com/YassenAli/Online-Library-by-C-sharp}{(GitHub Repository)}  \\
\textbullet{}\hspace{2mm} Designed and implemented an online library system with a user-friendly GUI using C\#.  \\
\textbullet{}\hspace{2mm} Managed user authentication, book inventory, and borrowing functionalities.

\textbf{Learning Management System (LMS)} \href{https://github.com/YassenAli/Learning-Management-System-LMS}{(GitHub Repository)}  \\
\textbullet{}\hspace{2mm} Developed a Java-based web application to manage and organize online courses, assessments, and user interactions.  \\
\textbullet{}\hspace{2mm} Implemented features such as course creation, user management, assessments, performance tracking, and notifications.

\textbf{Command Line Interpreter} \href{https://github.com/YassenAli/Command-Line-Interpreter}{(GitHub Repository)}  \\
\textbullet{}\hspace{2mm} Implemented a basic Command Line Interpreter (CLI) in Java, similar to a Unix/Linux shell.  \\
\textbullet{}\hspace{2mm} Supported various system and internal commands and included comprehensive unit testing using JUnit.

\textbf{CPU Schedulers Simulator} \href{https://github.com/YassenAli/CPU-Schedulers-Simulator}{(GitHub Repository)}  \\
\textbullet{}\hspace{2mm} Built a CPU Scheduling Simulator in Java to demonstrate and simulate various CPU scheduling algorithms.  \\
\textbullet{}\hspace{2mm} Algorithms implemented include Priority Scheduling, Shortest Job First (SJF), Shortest Remaining Time First (SRTF), and custom algorithms.

\textbf{React Calculator App} \href{https://github.com/YassenAli/Calculator}{(GitHub Repository)}  \\
\textbullet{}\hspace{2mm} Developed a user-friendly calculator app with React.js.  \\
\textbullet{}\hspace{2mm} Supported basic arithmetic operations, memory functions, and various special mathematical functions.

\textbf{Sudoku Game} \href{https://github.com/YassenAli/Sudoku-Game}{(GitHub Repository)}  \\
\textbullet{}\hspace{2mm} Implemented a Sudoku game using JavaScript.  \\
\textbullet{}\hspace{2mm} Developed the logic for generating and solving puzzles and ensured a responsive user interface.

\textbf{Games by Python}  \\
\textbullet{}\hspace{2mm} Designed many classic games (e.g., Tic-Tac-Toe, Hangman, Nim, and Number Scrabble) in Python with modular architecture.

% \vspace{2mm}

\section*{Languages \& Interests}
\textbf{Languages:} English (B2), Arabic (Native) \\
\textbf{Interests:} Data Engineering, Cybersecurity, Problem-Solving, Web Technologies

\end{document}



% 
% \section*{Experience}
% \textbf{Web Development Intern, Bee Interactive} \hfill Jul 2024 -- Oct 2024 \
% \textbullet{} Spearheaded development on Libri (library system), Eventi (event booking system), and Montri (online course platform). \
% \textbullet{} Improved system performance by optimizing queries, reducing response times by 30%. \
% \textbullet{} Developed reusable front-end components, enhancing scalability and maintainability.

% \textbf{Front-End Workshop Instructor, Minders (AC Volunteer Member)} \hfill Apr 2024 -- Oct 2024 \
% \textbullet{} Led hands-on workshops on front-end technologies, mentoring 100+ students. \
% \textbullet{} Designed structured learning modules, improving student engagement and comprehension. \
% \textbullet{} Facilitated collaborative projects, fostering teamwork and real-world problem-solving skills.

% \textbf{Front-End Developer, Minders} \hfill Feb 2024 -- Oct 2024 \
% \textbullet{} Built interactive applications such as a Sudoku game, portfolio website, and advanced CSS projects. \
% \textbullet{} Optimized UI/UX, improving user experience and accessibility across multiple devices.
% 