\documentclass[a4paper,10pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{fontawesome}
\usepackage{xcolor}

% \hypersetup{
%     colorlinks=true,
%     linkcolor=black,
%     urlcolor=blue
% }

\begin{document}

\centerline{\Huge \textbf{Yassin Ali}}
\vspace{2mm}
\centerline{
  Egypt, Giza, El-Haram \textbullet{}
  \href{tel:+201155015659}{\faPhone\ +201155015659} \textbullet{}
  \href{mailto:yassinalilearning77076@gmail.com}{\faEnvelope\ \texttt{yassinalilearning77076@gmail.com}} \textbullet{}
  \href{https://www.linkedin.com/in/yassin-ali-10497a252/}{\faLinkedinSquare\ Yassin Ali} \textbullet{}
  \href{https://github.com/YassenAli}{\faGithub\ YassenAli}
}

% \vspace{2mm}

\section*{Summary}
Results-driven third-year Computer Science student specializing in full-stack web development, object-oriented programming, and data structures. Proven ability to lead technical projects, mentor teams, and deliver scalable, user-focused applications. Skilled in leveraging modern frameworks to achieve tangible results, with experience in streamlining processes and exceeding expectations.

% \vspace{2mm}

\section*{Education}
\textbf{Faculty of Computers and Artificial Intelligence, Cairo University} \hfill Class of 2026 \\
Bachelor of Computer Science (Information Systems Department) \\
Relevant Coursework: Databases, Data Structures \& Algorithms, Object-Oriented Programming, Logic Design, Web Development, Software Engineering, Operating Systems, Networking, High-Performance Computing

% \vspace{2mm}

\section*{Experience}
\textbf{Web Development Intern, Bee Interactive} \hfill Jul 2024 -- Oct 2024 \\
\textbullet{}\hspace{2mm} Collaborated with a full-stack team on projects such as Libri (library system), Eventi (event booking system), and Montri (online course platform).  \\
\textbullet{}\hspace{2mm} Developed user-friendly interfaces and ensured seamless functionality across platforms.  \\
\textbullet{}\hspace{2mm} Delivered individual assignments including interactive applications.

\textbf{Front-End Workshop Instructor, Minders (AC Volunteer Member)} \hfill Apr 2024 -- Oct 2024 \\
\textbullet{}\hspace{2mm} Led front-end workshops, prepared educational materials, and coordinated team assignments.  \\
\textbullet{}\hspace{2mm} Acted as a liaison between students and workshop facilitators.

\textbf{Front-End Developer, Minders} \hfill Feb 2024 -- Oct 2024 \\
\textbullet{}\hspace{2mm} Worked on diverse front-end development tasks such as a Sudoku game, a personal portfolio, and advanced CSS tasks.

% \vspace{2mm}

\section*{Technical Skills}
\textbf{Programming Languages:} Python, JavaScript, Java, C++, SQL, HTML, CSS \\
\textbf{Frameworks \& Libraries:} React.js, Node.js, Django, Spring Boot \\
\textbf{Tools \& Platforms:} Git, GitHub, MySQL, MongoDB, Sequelize ORM, JUnit \\
\textbf{Other Skills:} Agile Development, Responsive Design, Version Control

\section*{Languages \& Interests}
\textbf{Languages:} English (B2), Arabic (Native) \\
\textbf{Interests:} Data Engineering, Cybersecurity, Problem-Solving, Web Technologies

\end{document}
