\documentclass[a4paper,10pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{fontawesome}
\usepackage{xcolor}

\begin{document}

\centerline{\Huge \textbf{Yassin Ali}}
\vspace{2mm}
\centerline{\large Software Engineer}
\vspace{2mm}
\centerline{
  Egypt, Giza, El-Haram \textbullet{}
  \href{tel:+201155015659}{\faPhone\ +20~115~501~5659} \textbullet{}
  \href{mailto:yassinalilearning77076@gmail.com}{\faEnvelope\ \texttt{yassinalilearning77076@gmail.com}} \textbullet{}
  \href{https://www.linkedin.com/in/yassin-ali-10497a252/}{\faLinkedinSquare\ Yassin Ali} \textbullet{}
  \href{https://github.com/YassenAli}{\faGithub\ YassenAli}
}

% \vspace{2mm}

\section*{Summary}
Third-year Computer Science student at Cairo University with hands-on experience in full-stack development and software engineering. Proficient in JavaScript, Python, and Java ecosystems including React.js, Node.js, and Django frameworks. Demonstrated success in team leadership, application development lifecycle, and technical mentorship. Core competencies in system design, database architecture, and performance optimization.

% \vspace{2mm}

\section*{Education}
\textbf{Faculty of Computers and Artificial Intelligence, Cairo University, Egypt} \hfill Class of 2026 \\
Bachelor of Computer Science. \\
Department: Information Systems. \\
Relevant Coursework: Databases, Data Structures \& Algorithms, OOP, Logic Design, Web Development, Software Engineering, Operating Systems, Networking, High-Performance Computing, Data Warehousing.

% \vspace{2mm}

\section*{Experience}
\textbf{Web Development Intern, Bee Interactive} \hfill Jul 2024 -- Oct 2024 \\
\textbullet{}\hspace{2mm} Collaborated with a full-stack team on projects such as Libri (library system), Eventi (event booking system), and Montri (online course platform).  \\
\textbullet{}\hspace{2mm} Developed user-friendly interfaces and ensured seamless functionality across platforms.  \\
\textbullet{}\hspace{2mm} Delivered individual assignments including interactive applications.

\textbf{Front-End Workshop Instructor, Minders (AC Volunteer Member)} \hfill Apr 2024 -- Oct 2024 \\
\textbullet{}\hspace{2mm} Led front-end workshops, prepared educational materials, and coordinated team assignments.  \\
\textbullet{}\hspace{2mm} Acted as a liaison between students and workshop facilitators.

\textbf{Front-End Developer, Minders} \hfill Feb 2024 -- Oct 2024 \\
\textbullet{}\hspace{2mm} Worked on diverse front-end development tasks such as a Sudoku game, a personal portfolio, and advanced CSS tasks.

% \vspace{2mm}

\section*{Technical Skills}
\textbf{Programming Languages:} Python, JavaScript, Java, C++, SQL, HTML, CSS \\
\textbf{Frameworks \& Libraries:} React.js, Node.js, Django, Spring Boot \\
\textbf{Tools \& Platforms:} Git, GitHub, MySQL, MongoDB, Sequelize ORM, JUnit \\
\textbf{Other Skills:} Agile Development, Responsive Design, Version Control

\section*{Languages \& Interests}
\textbf{Languages:} English (B2), Arabic (Native) \\
\textbf{Interests:} Data Engineering, Cybersecurity, Problem-Solving, Web Technologies

\end{document}
